Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-03 p2/axioms.tex
Restating rules for proofs

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecrefs{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
TODO elaborates this approach.

@@

\item\mlabel{ax_separate_commute}
Commands on incomparable nodes commute:
$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.

\item\mlabel{ax_separate_nobreaks}
Commands on incomparable nodes also do not break all filesystems:
$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.

\item\mlabel{ax_same_breaks}
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.

\item\mlabel{ax_same_emptyseq}
Commands on the same node are extended by an empty sequence if their types are compatible,
and their outer types represent an assertion command:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
$[x]=[\empt]$ and $[w]=[\empt]$,
or $[x]=[\vald]$ and $[w]=[\vald]$.

\item\mlabel{ax_same_singlec}
Command pairs on the same node are equivalent to a single command if their types are compatible,
and their outer types do not represent an assertion command:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
neither $[x]=[\empt]$ and $[w]=[\empt]$,
nor $[x]=[\vald]$ and $[w]=[\vald]$.

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxypnv\cc\czwnv \equiv \cbrk$ where $\cxypnv\cc\czwnv$ is not a construction pair, 
$\cxypnv\neq\cdda{\pn}$ and $\czwnv\neq\cbba{n}$.

\item\mlabel{ax_directparent_breaks}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwpnv \equiv \cbrk$ where $\cxynv\cc\czwpnv$ is not a destruction pair,
$\cxynv\neq\cbba{n}$ and $\czwpnv\neq\cdda{\pn}$.

\item\mlabel{ax_distantrel_breaks}
Commands on distant relatives break all filesystems
if the commands do not simply assert a directory at the ancestor
or an empty node at the descendant:
$\cxynnv\cc\czwnv \equiv \cbrk$
and $\czwnv\cc\cxynnv \equiv\cbrk$
where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.

\item\mlabel{ax_child_assert}
An assertion command can be freely added on a descendant node
next to a command that does not simply assert a directory:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxynnv\neq\cdda{\nn}$.

\item\mlabel{ax_parent_assert}
An assertion command can be freely added on an ancestor node
next to a command that does not simply assert an empty node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxynv\neq\cbba{n}$.

\item\mlabel{ax_assert}
All assertion commands can be removed as the empty sequence extends them:
$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.

>>>>

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecrefs{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
TODO elaborates this approach.
In \cref{axiom_proof} we offer proofs of each of the
\emph{\namecrefs{ax_separate_commute}} based on our model of filesystems.

@@

\item\mlabel{ax_separate_commute}
\axaxseparatecommute

\item\mlabel{ax_separate_nobreaks}
\axaxseparatenobreaks

\item\mlabel{ax_same_breaks}
\axaxsamebreaks

\item\mlabel{ax_same_emptyseq}
\axaxsameemptyseq

\item\mlabel{ax_same_singlec}
\axaxsamesinglec

\item\mlabel{ax_directchild_breaks}
\axaxdirectchildbreaks

\item\mlabel{ax_directparent_breaks}
\axaxdirectparentbreaks

\item\mlabel{ax_distantrel_breaks}
\axaxdistantrelbreaks

\item\mlabel{ax_child_assert}
\axaxchildassert

\item\mlabel{ax_parent_assert}
\axaxparentassert

\item\mlabel{ax_assert}
\axaxassert
